### 2021-03-24 paper/00_main.tex
Added paper template.

% \documentclass[review]{cvpr}
\documentclass[final]{cvpr}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
% \setcounter{page}{4321} % For final version only

\begin{document}

%%%%%%%%% TITLE
\title{AI604 term project paper template}

\author{Except for the proposal, do not provide student information (e.g., name and student ID)
}

\maketitle

\begin{abstract}
Abstract is optional. This will not affect the final score.
\end{abstract}

\section{Guideline: Proposal}

Feel free to describe your idea. We expect that the proposal includes \textit{the definition of the task}, \textit{dataset}, and \textit{tentative plan for the project}.

Please note that you can change the project topic after the proposal. However, we strongly discourage you from changing the topic after progress 1.

\section{Guideline: Progress 1 / 2}

After the proposal, we will check the progress of your project two times. You should submit the progress reports, and the reports should contain the contents of the proposal, \textit{related work} (and \textit{previous work} if exist), \textit{method}, and \textit{experiment}. It is okay to omit the result.

Other students will review your progress reports, and it is in a fully \textit{double-blind} manner. Each team will receive three or four reviews, and the review scores will affect your final score. For fair evaluation, students who have the same advisor do not review each others' work, and also \textbf{you will judge the reviews' review!} In the case of Progress 1, every team should submit \textit{author response}. The length of the response is up to one page. We provide the template for the author response; please check \texttt{01\_rebuttal.tex}.

\section{Guideline: Final}

The final report should contain the contents of the proposal and the progress reports, \textit{result}, and \textit{etc}. The length of the paper is up to nine pages except for \textit{reference}. Reference is optional, but we strongly recommend you to add the reference.

There will be a project presentation session at the end of the semester. Further instructions will be announced later.

\section{Etc}

If you have a question, send us an e-mail or a message to the Kakao open chat room.

{\small
\bibliographystyle{ieee_fullname}
\bibliography{reference}
}

\end{document}

### 2021-03-28 paper/00_main.tex
Edited proposal before submission (needs to be reviewed.

@@
 %%%%%%%%% TITLE
-\title{AI604 term project paper template}
-
-\author{Except for the proposal, do not provide student information (e.g., name and student ID)
-}
+\title{Tentative: Vision Transformer for Biomedical Image Segmentations}
+\author{Bedionita Soro (20205677), Ying Hui Tan (20204871), Oh Joon Kwon (20213044)}
 
@@
 \begin{abstract}
-Abstract is optional. This will not affect the final score.
+Segmentation is crucial in biomedical images analysis for detecting diseases such as breast cancer and pulmonary diseases.
+However, manually detecting a specific cell or organ can be laborious and difficult because it requires professional medical knowledge.
+Moreover, the complexity of images (artifacts, other cells or organs) can add to errors that can be potentially harmful in medical practices.
+There have been numerous attempts to automate this procedure, but most recently, deep learning based automatic segmentation methods such as U-Net and its variants have gained attention.
+Nevertheless, it requires a large amount of training data, and histological images contains much noise that degrades the performance.
+In this paper, we exploit  recent advanced methods in deep learning and propose a multi domain approach that can semantically segment histology images for breast cancer detection and extend it to lesion segmentation in COVID-19 CT scan, exploiting domain adaptation techniques.
+The proposed method makes use of the recent state-of-the-art computer vision methods such as Vision Transformer (ViT).
 \end{abstract}
 
-\section{Guideline: Proposal}
+\section{Introduction}
+Semantic segmentation is crucial in biomedical image analytics, yet requires heavy workload for manual annotation.
+Segmentation task can become very difficult for the pathologists even with high-expertise due to other organs, artifacts, and fatigue \cite{KRUPINSKI20061543}.
+This is because they often have to screen all the whole slide images (WSI) to find regions of interest with abnormal tissues or organs \cite{Randell01}.
+Recently, several semantic segmentation methods exploiting deep learning have been developed for histo-pathological images or organ segmentation \cite{lei2020medical}.
+However, most of these existing methods not only focus on a specific organ or tissue \cite{chan2019histosegnet}, but they have not largely investigated domain adaptation techniques with organs from different domains.
 
-Feel free to describe your idea. We expect that the proposal includes \textit{the definition of the task}, \textit{dataset}, and \textit{tentative plan for the project}.
+In this paper, we propose a semantic segmentation method with Transformer architecture \cite{vaswani2017attention} to semantically segment and identify different type of cancer regions in the WSI for breast cancer detection.
+We then extend this approach to segment COVID-19's lesion in lung \cite{9385788} using domain adaptation.
+This allows us a model to generalize over totally different domains with less effort.
 
-Please note that you can change the project topic after the proposal. However, we strongly discourage you from changing the topic after progress 1.
+\subsection{Problem and Contributions}
+Organ segmentation is crucial for disease detection and treatment.
+Breast cancer and COVID-19 are among the common diseases that can be helped with automatic segmentation.
+Even though there exists some academic works on classifying cancer diseases in the WSI of breasts, those models perform below par compared to deep learning methods in computer vision.
+On the other hand, it is very challenging to build a model specific to that new disease due to the lack of data for COVID-19.
+Therefore, there is a need for domain adaptation in medical image segmentation.
 
-\section{Guideline: Progress 1 / 2}
+The first objective of this study is to propose a deep neural network model that will efficiently and accurately identify different regions of interest in the WSI of breast for different type of cancer diseases detection.
+The second objective is to exploit the knowledge obtained on the breast cancer dataset to perform COVID-19 lesion segmentation through domain adaptation techniques.
+The performance of the proposed method will be compared with other state-of-the-art models \cite{chan2019histosegnet, chen2021transunet, Fu_2018, He2020.04.13.20063941} on publicly available datasets.
+The contributions of this work can be summarized as follows:
+\begin{itemize}
+    \item We propose a semantic segmentation method for breast cancer to identify type of regions of interest,
+    \item We also investigate the problem COVID-19's lung lesion segmentation which is a hot topic with less available data.
+In order to address the lack of data, domain adaptation will be explored as an option, adapting histological images to the COVID-19 patient CT scans.
+    \item The proposed method exploits the advantage of Vision Transformer \cite{dosovitskiy2020image}, which makes this the first work that uses Transformer in histological images segmentation for breast cancer detection,
+    \item This approach will reduce the burden of manually detecting the regions of interest in histopathology images.
+It will provide a way to mitigate the problem of limited data in images segmentation for new diseases.
+    \item We expect to compare the proposed method against some recent state-of-art methods \cite{dosovitskiy2020image,touvron2021training}.
+    \item This work aims to contribute to the development of automatic healthcare systems that is becoming essential with the ongoing pandemic.
+\end{itemize}
 
-After the proposal, we will check the progress of your project two times.
+% \section{related work}
+
+\section{Method}
+The proposed method integrates recent state-of-the-art deep learning model in image classification known as Vision Transformer (ViT) \cite{dosovitskiy2020image}.
+Transformer, proposed by Vaswani et al.\cite{vaswani2017attention}, makes use of multi-head self-attention mechanism that can easily be scaled with large datasets.
+While the widely used methods in image segmentation uses convolutional neural networks (CNN) as their building blocks, parameter sharing nature of CNNs often introduces inductive bias when adapted to different data domains \cite{cohen2017inductive}.
+This leads to degraded model performance in these domains.
+
+Pretrained Transformer models have been shown to be flexible when fine-tuned for down-stream tasks, both in natural language processing and computer vision.
+While it can be computationally expensive to pretrain the models on large datasets, Transformers often excel at adapting to different domains which makes it ideal for transfer learning and possibly domain adaptation.
+Moreover, the nature of semantic segmentation task requires the contextual understanding of the relationship among image regions.
+The self-attention mechanism that is built into Transformers could boost the model performance in such a task.
+
+\begin{figure}[h!]
+\begin{center}
+% \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=0.8\linewidth]{media/roi1.PNG}
+\end{center}
+   \caption{Block diagram of the model for WSIs segmentation and classification}
+\label{fig:roi}
+% \label{fig:onecol}
+\end{figure}
+
+As shown in Figure \ref{fig:roi}, the first step of in this work is to build a deep learning model that will receive patches of WSIs and output the probabilities of the dominant diseases as well as the segmented version of the WSIs where each tissue type is mapped to the region of interest.
+Both segmentation and classification will be combined to achieve this objective.
+For the lung lesion segmentation, the same model will be used as a baseline.
+To that end, different techniques for domain adaptation will be explored such as self-supervised learning and transfer learning.
+
+\subsection{Evaluation metric}
+To evaluate the proposed method, we aim to use two different metrics for prediction and segmentation.
+The prediction level metric consists of: \textit{F1}, \textit{precision}, and the \textit{sensitivity} as defined in \ref{metric1}
+
+\begin{equation}
+\begin{split}
+   \text{F1} & = \frac{2TP}{2TP+FP+ FN}, \\
+   \text{Sensitivity} & = \frac{TP}{TP+FN}, \\
+   \text{Precision} & = \frac{TP}{TP+FP} ,
+   \label{metric1}
+\end{split}
+\end{equation}
+where $TP$, $FP$ and $FN$ are true positive, false positive and false negative, respectively.
+
+For segmentation level metric, the Jacard index or DICE's coefficient $D$ defined in equation \ref{metric2},
+\begin{equation}
+    D(\hat{Y},Y)=2\frac{|\hat{Y} \cap Y|}{|\hat{Y} \cup Y|},
+    \label{metric2}
+\end{equation}
+where $\hat{Y}$ and $Y$ are the predicted region from the model and the ground truth region of input image, respectively.
+
+\section{Data}
+The model will be trained and assessed on several datasets.
+The first dataset used in this study was introduced in \cite{10.1093/bioinformatics/btz083}.
+It consists of 151 hematoxylin and eosin strained whole-slide images (WSIs) from histologically confirmed cases of breast cancer.
+The dataset is available on the Cancer Genome Atlas.
+The mean and the standard deviation of the region of interest are respectively 1.18mm\textsuperscript{2} and 0.80mm\textsuperscript{2}.
+The second dataset considered is from \cite{zhao2020COVID-CT-Dataset} which consists of 349 COVID-19 CT images from 216 patients and 463 non-COVID-19 CTs.
+In addition to that we will used another publicly available dataset published by China National Center for Bioinformation \cite{Gunraj2020} consisting of 650 scans across 150 patients with various stages of COVID.
+
+\newpage 
+\section{Tentative plans}
+\begin{figure}[h!]
+\begin{center}
+% \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=1.0\linewidth]{media/chart.png}
+\end{center}
+   \caption{Tentative schedule}
+\label{fig:schedule}
+% \label{fig:onecol}
+\end{figure}
+
+%\cite{Randell}.
+% \cite{10.1093/bioinformatics/btz083}
+
+% \section{Guideline: Progress 1 / 2}
+
+% After the proposal, we will check the progress of your project two times.
 You should submit the progress reports, and the reports should contain the contents of the proposal, \textit{related work} (and \textit{previous work} if exist), \textit{method}, and \textit{experiment}.
@@
 
-Other students will review your progress reports, and it is in a fully \textit{double-blind} manner.
+% Other students will review your progress reports, and it is in a fully \textit{double-blind} manner.
 Each team will receive three or four reviews, and the review scores will affect your final score.
@@
 
-\section{Guideline: Final}
+% \section{Guideline: Final}
 
-The final report should contain the contents of the proposal and the progress reports, \textit{result}, and \textit{etc}.
+% The final report should contain the contents of the proposal and the progress reports, \textit{result}, and \textit{etc}.
 The length of the paper is up to nine pages except for \textit{reference}.
@@
 
-There will be a project presentation session at the end of the semester. Further instructions will be announced later.
+% There will be a project presentation session at the end of the semester. Further instructions will be announced later.
 
-\section{Etc}
+% \section{Etc}
 
-If you have a question, send us an e-mail or a message to the Kakao open chat room.
+% If you have a question, send us an e-mail or a message to the Kakao open chat room.
 

### 2021-03-28 paper/00_main.tex
Made some changes according to feedback.
Made last minute changes before submisison.

@@
 %%%%%%%%% TITLE
-\title{Tentative: Vision Transformer for Biomedical Image Segmentations}
+\title{Vision Transformer for Biomedical Image Segmentation}
 \author{Bedionita Soro (20205677), Ying Hui Tan (20204871), Oh Joon Kwon (20213044)}
@@
 Semantic segmentation is crucial in biomedical image analytics, yet requires heavy workload for manual annotation.
-Segmentation task can become very difficult for the pathologists even with high-expertise due to other organs, artifacts, and fatigue \cite{KRUPINSKI20061543}.
-This is because they often have to screen all the whole slide images (WSI) to find regions of interest with abnormal tissues or organs \cite{Randell01}.
+Segmentation task can become very difficult for the pathologists even with high-expertise due to other organs, noise and artifacts\cite{KRUPINSKI20061543}.
+Moreover, human annotators tend to be fatigued because they often have to screen all the whole slide images (WSI) to find regions of interest with abnormal tissues or organs \cite{Randell01}.
 Recently, several semantic segmentation methods exploiting deep learning have been developed for histo-pathological images or organ segmentation \cite{lei2020medical}.
@@
 While the widely used methods in image segmentation uses convolutional neural networks (CNN) as their building blocks, parameter sharing nature of CNNs often introduces inductive bias when adapted to different data domains \cite{cohen2017inductive}.
-This leads to degraded model performance in these domains.
+This leads to degraded model performance in inexperienced domains.
 
-Pretrained Transformer models have been shown to be flexible when fine-tuned for down-stream tasks, both in natural language processing and computer vision.
+Pretrained Transformer models have been shown to be flexible when fine-tuned for down-stream tasks, both in natural language processing and computer vision \cite{devlin2019bert,radford2019language}.
 While it can be computationally expensive to pretrain the models on large datasets, Transformers often excel at adapting to different domains which makes it ideal for transfer learning and possibly domain adaptation.
@@
 
-As shown in Figure \ref{fig:roi}, the first step of in this work is to build a deep learning model that will receive patches of WSIs and output the probabilities of the dominant diseases as well as the segmented version of the WSIs where each tissue type is mapped to the region of interest.
-Both segmentation and classification will be combined to achieve this objective.
+As shown in Figure \ref{fig:roi}, the first step of in this work is to build a deep learning model with Vision Transformers as input that will receive patches of WSIs and encodes the image, then outputs the probabilities of the dominant diseases as well as the segmented version of the WSIs where each tissue type is mapped to the region of interest.
+Both segmentation and classification objective functions will be combined to achieve this taskz.
 For the lung lesion segmentation, the same model will be used as a baseline.
@@
 \newpage 
-\section{Tentative plans}
+\section{Tentative plan}
 \begin{figure}[h!]

### 2021-04-25 code/classification/preprocess.py
Uploaded experiment codes.

@@ -1,0 +1,179 @@
+import os
+import glob
+import random
+
+import torch
+import albumentations as alb
+import numpy as np
+
+from tqdm import tqdm
+import cv2
+from torch.utils.data import Dataset, DataLoader
+from typing import Dict, List, Tuple, Optional, Union
+
+CLASSES = \
+    [
+        ('DC', 'ductal_carcinoma'),
+        ('LC', 'lobular_carcinoma'),
+        ('MC', 'mucinous_carcinoma'),
+        ('PC', 'papillary_carcinoma'),
+        ('A', 'adenosis'),
+        ('F', 'fibroadenoma'),
+        ('PT', 'phyllodes_tumor'),
+        ('TA', 'tubular_adenoma')
+    ]
+
+LABELS = {k[0]: v for v, k in enumerate(CLASSES)}
+
+# 0 if BENIGN, 1 if MALIGNANT
+BIN_LABELS = {k[0]: 1 if k[0] in ('DC', 'LC', 'MC', 'PC') else 0 for v, k in enumerate(CLASSES)}
+
+
+"""
+    NOTE: The classes can be put into sub-classes.
+
+    MALIGNANT = \
+        [
+            ('DC', 'ductal_carcinoma'),
+            ('LC', 'lobular_carcinoma'),
+            ('MC', 'mucinous_carcinoma'),
+            ('PC', 'papillary_carcinoma')
+        ]
+    BENIGN = \
+        [
+            ('A', 'adenosis'),
+            ('F', 'fibroadenoma'),
+            ('PT', 'phyllodes_tumor'),
+            ('TA', 'tubular_adenoma')
+        ]
+"""
+
+class BreakHisDataset(Dataset):
+    def __init__(self, num_classes: int, data_path: str='./combined', magnification: str='40X'):
+        super().__init__()
+
+        paths = os.path.join(data_path, magnification, '*.png')
+        self.files = glob.glob(paths)
+        
+        # Function for getting the label
+        if num_classes == 8:
+            self.get_label = lambda x: LABELS.get(x.split('_')[2].split('-')[0])
+        else:
+            self.get_label = lambda x: BIN_LABELS.get(x.split('_')[2].split('-')[0])
+ 
+    def __len__(self):
+        return len(self.files)
+
+    def __getitem__(self, idx):
+        f = self.files[idx]
+        # np.ndarray
+        img = cv2.imread(f)
+        img = cv2.cvtColor(img, cv2.COLOR_BGR2RGB)
+        # int
[…]

### 2021-04-25 code/classification/train.py

@@ -1,0 +1,318 @@
+import os
+import sys
+import yaml
+import torch
+import wandb
+import timm
+import numpy as np
+import matplotlib.pyplot as plt
+
+from math import ceil
+from tqdm import tqdm
+
+from dataclasses import dataclass, field, InitVar
+from typing import Dict, List, Union, Optional
+from simple_parsing import ArgumentParser
+
+from torch import nn
+from torch.utils.data import DataLoader
+from torch.utils.data.dataset import random_split
+
+from accelerate import Accelerator
+from transformers import get_scheduler
+
+from preprocess import FeatureExtractor, BatchCollector, BreakHisDataset, LABELS, BIN_LABELS
+
+@dataclass
+class Arguments:
+    data_dir: str = field(default='combined')
+    magnification: str = field(default='40X')
+    augmentation: bool = field(default=False)
+    train_split: float = field(default=0.7)
+
+    model_class: str = field(default='vit_base_pytorch16_224')
+    pretrained: bool = field(default=False)
+    checkpoint: Optional[str] = field(default=None)
+    num_classes: int = field(default=8)
+    seed: int = field(default=42)
+
+    device: str = field(default='cuda')
+    amp: bool = field(default=False)
+
+    num_epochs: int = field(default=3)
+    batch_size: int = field(default=1)
+
+    lr: float = field(default=3e-5)
+    eps: float = field(default=1e-8)
+    beta_1: float = field(default=0.99)
+    beta_2: float = field(default=0.999)
+    weight_decay: float = field(default=1e-5)
+    grad_clipping: float = field(default=False)
+    grad_max_norm: float = field(default=1.0)
+    grad_accumulation_steps: int = field(default=1)
+
+    scheduler: Optional[str] = field(default=None)
+    num_warmup_steps: Optional[int] = field(default=400)
+
+    log_interval: int = field(default=15)
+    save_model: bool = field(default=False)
+
+    config: InitVar[Dict] = field(default=dict())
+
+    def __post_init__(self, config: Dict):
+        for k, v in config.items():
+            try:
+                if v is not None:
+                    self.__setattr__(k, v)
+                # else:
+                #     self.__setattr__(k, '')
+            except AttributeError:
+                raise Exception('No config parameter {} found ...'.format(k))
+
[…]

### 2021-04-25 code/classification/download.sh
Added download script

@@ -1,0 +1,1 @@
+gdown https://drive.google.com/u/1/uc?id=1bd60s98V3W00R_N7tvOE5pfoDaf8lpfv&export=download

### 2021-04-25 code/crowdsourcing/download_crowdsourcing.sh
download script for crowdsourcing dataset

@@ -1,0 +1,7 @@
+#!/bin/sh
+
+echo Installing Boto3...
+pip3 install boto3 --user
+
+echo Download CrowdSourcing Dataset: Images, Masks, Metadata...
+python3 download_from_s3.py

### 2021-04-25 code/crowdsourcing/download_from_s3.py

@@ -1,0 +1,34 @@
+"""
+Run this script to download CrowdsourcingDataset-Amgadetal2019 from S3.
+"""
+
+import boto3
+import os
+
+AWS_ACCESS_KEY_ID = "AKIASJXRCGLKGJYCUFDL"
+AWS_SECRET_KEY = "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"
+BUCKET_NAME = "ai604"
+PREFIXS = [
+    "dataset/images/",
+    "dataset/masks/",
+    "dataset/meta/"
+]
+
+s3 = boto3.resource('s3',aws_access_key_id=AWS_ACCESS_KEY_ID,aws_secret_access_key=AWS_SECRET_KEY)
+bucket = s3.Bucket(BUCKET_NAME)
+
+for prefix in PREFIXS:
+    objects = bucket.objects.filter(Prefix=prefix)
+    total = 3 if (prefix == "dataset/meta/") else 151
+    
+    if not os.path.isdir(prefix):
+        os.makedirs(prefix)
+    
+    print("\nStart downloading " + prefix + "...")
+    for i, obj in enumerate(objects):
+        path, filename = os.path.split(obj.key)
+        if filename == '':
+            continue
+        bucket.download_file(obj.key, obj.key)
+        progress = i*100/total
+        print("Progress: %.2f"%progress + " | Data: " + filename)

### 2021-04-25 code/classification/preprocess.py
Fixed some bugs.

@@ -49,11 +49,17 @@ BIN_LABELS = {k[0]: 1 if k[0] in ('DC', 'LC', 'MC', 'PC') else 0 for v, k in enu
 """
 
 class BreakHisDataset(Dataset):
-    def __init__(self, num_classes: int, data_path: str='./combined', magnification: str='40X'):
+    def __init__(self, num_classes: int, data_path: str='./combined', magnification: str='40X', files: Optional[List]=None):
         super().__init__()
 
-        paths = os.path.join(data_path, magnification, '*.png')
-        self.files = glob.glob(paths)
+        self.magnification = magnification
+        self.num_classes = num_classes
+
+        if files is not None:
+            self.files = files
+        else:
+            paths = os.path.join(data_path, magnification, '*.png')
+            self.files = glob.glob(paths)
         
         # Function for getting the label
         if num_classes == 8:
@@ -77,6 +83,11 @@ class BreakHisDataset(Dataset):
                 'images': np.array(img / 255.0, dtype=np.float32),
                 'labels': lbl
             }
+
+    def __add__(self, other):
+        assert self.num_classes == other.num_classes
+        self.files.extend(other.files)
+        return self
 
 class BatchCollector:
     """

### 2021-04-25 code/classification/train.py

@@ -1,6 +1,8 @@
 import os
 import sys
 import yaml
+import random
+
 import torch
 import wandb
 import timm
@@ -68,6 +70,15 @@ class Arguments:
                 #     self.__setattr__(k, '')
             except AttributeError:
                 raise Exception('No config parameter {} found ...'.format(k))
+
+def set_seed(seed: int):
+    torch.manual_seed(seed)
+    torch.cuda.manual_seed(seed)
+    torch.cuda.manual_seed_all(seed) # if use multi-GPU
+    torch.backends.cudnn.deterministic = True
+    torch.backends.cudnn.benchmark = False
+    np.random.seed(seed)
+    random.seed(seed)
 
 def plot_confusion_matrix(logits: "torch.Tensor", labels: "torch.Tensor", num_classes: int):
     label_dict = {'B': 0, 'M': 1}
@@ -146,11 +157,12 @@ def train(
     step = 0
 
     model.to(device)
+    
+    train_losses = list()
+    valid_losses = list()
     for epoch in range(args.num_epochs):
-        train_losses = list()
-        valid_losses = list()
         # Train
-        mean_train_loss = 0
+        tot, mean_train_loss = 0, 0
         model.train()
         for batch in train_loader:
             current_progress = step / len(train_loader)
@@ -163,7 +175,8 @@ def train(
 
             # Loss logging
             item_loss = losses.detach().item()
-            mean_train_loss = (item_loss * len(images)) / len(train_loader)
+            tot += len(labels)
+            mean_train_loss += (item_loss * len(images))
 
             losses /= args.grad_accumulation_steps
             accelerator.backward(losses)
@@ -185,12 +198,14 @@ def train(
                 # Update progress bar
                 progress.update(1)
             step += 1
-        train_losses.append(mean_train_loss)
+        train_losses.append(mean_train_loss / tot)
         
         # Validation
         mean_valid_loss, valid_logits, valid_labels = validate(model, valid_loader, valid_criterion, accelerator, step, current_progress, args)
         metric = compute_metric(valid_logits, valid_labels, args.num_classes)
         valid_losses.append(mean_valid_loss)
+
+        # Log Validation Metric
         wandb.log(metric, step=step, commit=False)
 
         acc = metric['top@1_acc']
@@ -199,17 +214,19 @@ def train(
             
             if args.save_model:
                 # Saving model
-                save_path = '{}_{}_{}_c{}_{}.pt'.format(
[…]

### 2021-04-25 paper/progress-1/01_rebuttal.tex
Added progress report 1.

\documentclass[rebuttal]{cvpr}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{0000} % Do not enter team number here
%\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\def\cvprPaperID{0000} % Do not enter team number here
\def\confYear{AI604 2021 spring}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{AI604 term project rebuttal / author response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

After receiving paper reviews, authors should submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.

Note that the author rebuttal is not visible to the reviewers. In other words, only TAs and the professor will read the rebuttal.

\subsection{Response length}

Author responses must be no longer than 1 page in length except for \textbf{References} and \textbf{Additional question}.

\subsection{Note}

Feel free to write the author response, and we recommend you not to spend your time so much on this. We aim to provide you a chance for improve your work by answering to the reviews.

%-------------------------------------------------------------------------
%\newpage

\section{Additional question}
Each team should answer the below questions for evaluating their reviewers.

\subsection{Question 1}
\begin{itemize}
    % 리뷰어 1 2 3 은 우리의 프로젝트 내용을 이해했다.
    \item The reviewer 1 understood our main idea and contributions. (Yes / Neutral / No)
    \item The reviewer 2 understood our main idea and contributions. (Yes / Neutral / No)
    \item ...
\end{itemize}

\subsection{Question 2}
\begin{itemize}
    % 리뷰어 1 2 3 은 우리에게 건설적인 피드백을 제공했다.
    \item The reviewer 1 provided constructive feedback or advice. (Yes / Neutral / No)
    \item The reviewer 2 provided constructive feedback or advice. (Yes / Neutral / No)
    \item ...
\end{itemize}

\subsection{Question 3}
\begin{itemize}
    % 기타 하고 싶은 말
    \item Other comments for TAs and the professor.
\end{itemize}

{\small
\bibliographystyle{ieee_fullname}
\bibliography{reference}
}

\end{document}

### 2021-04-25 paper/progress-1/00_main.tex
Added progress report 1.

\documentclass[review]{cvpr}
% \documentclass[final]{cvpr}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}

% Include other packages here, before hyperref.
\usepackage{multirow, multicol, booktabs}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx}
% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
% \setcounter{page}{4321} % For final version only

\begin{document}

%%%%%%%%% TITLE
\title{Breast Cancer Histopathological Images Segmentation and Classification using Vision Transformer}
\author{Bedionita Soro (20205677), Ying Hui Tan (20204871), Oh Joon Kwon (20213044)}

\maketitle

\begin{abstract}
Breast cancer is one of the wide-spread diseases in the world. Its detection at an early stage is crucial for increasing the chance of successful treatment of patients. However, pathologists often need to scan a large set of Whole Slide Images (WSIs) to identify the regions and the type of tissues, which is laborious task. There have been several deep learning based approaches to reduce the burden. Previous approaches made use of convolutional neural networks (CNNs) as feature extractor, which often struggle to generalize in different domains. Moreover, these approaches often takes sophisticated post-processing techniques and relies on patch-based technique treating each patch as an image. In this paper, we propose an end-to-end method that exploits the expressive capacity of Vision Transformer (ViT) and its variants. Our method can be put into three main phases. First, we build a classification model for breast cancer diagnosis. Second, we design a ViT based segmentation model for WSIs. Finally, we investigate the combination of these models for domain adaptation in other types of tissue segmentation. The preliminary experiment on BreakHis dataset has demonstrated the proposed method efficiently competes with the existing state-of-the-art results.
\end{abstract}

\section{Introduction}
Breast cancer \cite{7312934} is one of the most wide spread types of cancer whose detection and categorization is not straightforward even for expert pathologists \cite{Randell01}. In fact, pathologists have to scan a large set of Whole Slide Images (WSI), which can be in the order of gigapixels to localize the regions of tumor as well as to identify the type of tumor. To ensure that there is no malpractice, this has to be done in several magnification levels\cite{KRUPINSKI20061543}. Fortunately, due to recent advancements in deep learning specifically in pattern recognition\cite{russakovsky2015imagenet}, there has been a growing interest in applying deep learning to tissue segmentation and breast cancer classification using WSI\cite{lei2020medical,SRINIDHI2021101813}.

However, WSI are very large to segment with current deep learning methods without reducing the images' dimensions. Even though reducing the image size may have little effects on the cancer classification task (benign and malignant), detecting the region of interest through tissue type segmentation requires that images not be resized. To overcome such limitation, patch-based methods have been introduced\cite{7780635} for both tissues semantic segmentation and cancer classification. The patch-based methods consist of dividing WSI and ground-truth segmentation mask into small chunks of images. Patch-based approaches have been broadly investigated\cite{8451551} and are actually commonly used in large scale medical image segmentation. The extracted patches can be saved on the disk, but this can become impractical given the number of the images. Another challenge is that some patches do not have distinctive features and may require a good post-processing to achieve a desired outcome. Moreover, patches are treated independently without much regard to their global relationship in the whole image.

In this paper, we propose a new approach that exploits the current state-of-the-art Vision Transformer architecture to take advantage of WSI at once by considering each image as a sequence of patch tokens. Such an approach is fast to train for both cancer types classification and tissues type semantic segmentation with less effort in preprocessing and post-processing. Although similar architecture has been introduced in other medical images segmentation related work \cite{chen2021transunet}, to our knowledge, this is the first time this method is applied to WSI for breast cancer images segmentation and tissue classification. In most existing related work where Vision Transformer is used have been to exploit its pretrained feature extraction capability. We consider a similar approach as machine translation when dealing with semantic segmentation, where a sequence of images is given as input to produce a sequence of segmented masks.

The work of this paper can be divided into three parts. First, we propose Vision Transformer model for breast cancer classification. Second, we use similar base architecture for tissue type segmentation. Finally, we use the semantic segmentation model as feature extractor for cancer classification and investigate further domain adaptation. The contribution and the novelty of this paper are summarized as follows:
\begin{itemize}
    \item We propose the first Vision Transformer based cancer tissues segmentation and cancer types classification using WSI of breast. To our best knowledge, this approach has not yet been applied to WSI  and for large scale image segmentation and classification. 
    \item The proposed method require less postprocessing compared to the existing patch-based approaches.
    \item The proposed method is fast to train and achieve competitive results compared to existing complex convolution neural network model on classification tasks.
\end{itemize}

\section{Related work}
\noindent \textbf{WSI Classification.} Using WSI is one of the best ways to integrate deep learning in cancer diagnosis, specifically for breast cancer. In breast cancer diagnosis, the classification can be binary (benign or malignant) or multiclass. Hameed et al \cite{s20164373} used an ensemble of deep learning model such VGG16 and VGG19 to design a classifier model for non-carcinoma and carcinoma breast cancer histopathology images identification. However, this model is hard to train due to the complexity of VGG network. In the same vein of binary classification, Abdullah-Al  Nahid et al. \cite{2362108} employed CNN and LSTM among other features extraction methods to design a model that can accurately classify cancer type, benign or malignant. Similar approach has been proposed in \cite{alom2018breast} where they exploited the Inception recurrent CNN architecture to improve the performance on BreakHis dataset\cite{BENHAMMOU20209}.

On the other hand, some studies included the sub-classes of cancer in a multiclass classification approach \cite{Han2017}. \cite{9218931} proposed a comparison study of several deep learning approaches for breast cancer classification. Furthermore, \cite{BENHAMMOU20209} conducted a survey where they provided a performance analysis of existing state-of-the-art methods on BreakHis dataset. \cite{10.1371/journal.pone.0214587} is one of these best approaches for binary classification. They inserted squeeze and excitation module to a ResNet model and adjusted the optimization parameters to increase the classification performance. The existing methods are mostly based on patch-based approach where the challenges arise. One of the challenges is to distinguish informative patches from non-informative patches. It is also challenging to classify an image based on several sequences of patches. Additionally, dividing large images into patches and save to disk will triple the memory requirement (original, patches, and online execution). Our approach leverages all these challenges of existing method and can achieve competitive results. With the transformer architectures, we are still using patch-based approach but this method can take variable length of patches while extracting relevant image features with attention mechanism.\\
\\
\textbf{WSI Segmentation.} There is a large body of work on WSI segmentation\cite{vu2018methods}. Most recent works on WSI segmentation focus on deep learning\cite{10.3389/fmed.2019.00264}. However, applying deep learning for WSI segmentation is a challenging task because of the large size of the images where resizing is not generally recommended for accuracy. Therefore, most existing deep learning approaches exploit patch-based based segmentation\cite{PRIEGOTORRES2020113387, Fu_2018}. In \cite{10.1117/12.2581229}, active learning was used to enhance the performance of patch based WSIs segmentation. Similarly in \cite{Xulargescale2017}, pretrained deep convolutional neural network (CNN) was used to improve the performance of patch-based segmentation of brain WSIs for tumor detection. To investigate the deep learning model generalization, Mahendra Khened et al.\cite{khened2020generalized} proposed a deep learning framework for histological tissue segmentation. In their study, they explored different datasets including a breast cancer WSI dataset and evaluated the model's uncertainty and generalization performance against distributional shift.

Moreover, several studies such as \cite{Guofast2020} exclusively studies breast cancer WSI segmentation. In addition to WSI segmentation for cancer or disease detection, deep learning methods are being used for cancer classification from WSI\cite{XU2014591}, specifically for the  breast cancer. Most existing WSI segmentation methods are patch-based, therefore they require more additional post processing processing to combine the patches. Furthermore, some patches can be non-informative. Those methods commonly use deep CNN architectures which can slow the training process and difficult to train on computation resource limited devices. Transformer architectures can extract meaningful features from natural images. \\
\\
\textbf{Transformer.} Transformer architecture was first proposed by Vaswani et al.\cite{vaswani2017attention}. The essence of the architecture lies in the multi-headed self-attention (MHA) mechanism to learn the relationships among sequential tokens. MHA can be expressed as the following
\begin{equation}
\begin{split}
    \text{MHA}(Q, K,&\, V) =  \text{Concat}(A_1, \dots, A_h)W^O, \\[3mm]
    \text{where } A_i & := \text{Attention}(QW_i^Q, KW_i^K, VW_i^V) \\
        & = \text{softmax} \left( \frac{(QW_i^Q)(KW_i^K)^\top}{\sqrt{d_k}} \right) VW_i^V,
    \label{attention}
\end{split}
\end{equation}
where $Q, K, V$ are input query, key, value vectors, $W_i^Q, W_i^K \in \mathbb{R}^{d_{\text{model}}, d_k}, W_i^V \in \mathbb{R}^{d_{\text{model}}, d_v}$ are trainable query, key, value weights at the $i$-th attention head, $d_{\text{model}}$ the model dimension , $h$ number of heads, $d_k, d_v$ key and value dimension. By only using self-attention for processing sequential data, Transformer has shown state-of-the-art performance in numerous natural language processing tasks such as machine translation and sequence generation. Since its conception, Transformer architecture has been adapted to other domains.\\
\\
\textbf{Vision Transformer} Vision Transformer (ViT)\cite{dosovitskiy2020image} closely adapts Transformer Architecture for natural language processing for image classification. The concept consists of dividing the whole image into small chunks analogous to the sequence of tokens in machine translation. There are a few modifications from the original Transformer architecture for image domains:
\begin{enumerate}
    \item In order to circumvent the quadratic memory bottleneck, ViT takes in patches of images instead of pixels that are flattened then embedded via linear layer, essentially taking patches as tokens.
    \item Because of the sequential nature, ViT can take higher resolution inputs. However, position embeddings need to be interpolated for finetuning. This has been shown to be emprically effective in the subsequent downstream tasks. 
    \item As in the pretrained language model BERT, a classification token is appended before the patch tokens.
\end{enumerate}
Through extensive experiments, it has been proved that the ViT outperforms the existing state-of-the-art models in image classification tasks, thereby several variants of ViT have been proposed\cite{wu2021cvt,zhou2021deepvit}. Furthermore, ViT model can be a good feature extractor or encoder given that it has been trained on various type of datasets. Therefore, we apply this promising architecture to histological images segmentation and breast cancer classification.

% \begin{table}[ht]
% \centering
% \resizebox{\columnwidth}{!}{\begin{tabular}{c|c|c|c}
% \toprule
% Network & Salient Feature & Parameters & FLOP \\ \toprule
% AlexNet &  Deep & 61M & 1.5B \\ 
% VGG-16 & Fixed-size kernels & 138M & 19.6B \\
% Inception & Wide/parallel kernels & 43M & 2B \\
% ResNet-152 & Skip connection & 60M & 11B \\
% ViT & Transformer & 86M & \\
% \bottomrule
% \end{tabular}}
% \caption{Comparing number of trainable parameters and FLOPs according to model architectures. M stands for million and B billion.}
% \label{param}
% \end{table}

\section{Method}
\begin{figure}[ht]
\begin{center}
% \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.8\linewidth]{media/roi1.PNG}
\end{center}
   \caption{Block diagram of the model for WSIs segmentation and classification}
\label{fig:roi}
% \label{fig:onecol}
\end{figure}
Figure \ref{fig:roi} depicts the block diagram of the proposed method. Our approach can be decomposed into two main steps: first, we build a classification model based on ViT for breast cancer detection, then we build a model for WSI segmentation. We then combine those models to produce a multi tasks model. Another option we have is to apply domain adaptation to another organ segmentation dataset. 
\subsection{Classification}
\begin{figure}[ht]
\begin{center}
% \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   \includegraphics[width=0.8\linewidth]{media/classify.png}
\end{center}
   \caption{Block diagram of the model for WSI classification}
\label{fig:cls}
% \label{fig:onecol}
\end{figure}
In this section we begin with the classification model. Our first goal is to use the ViT to accurately predict the class of breast cancer given a whole slide image as input. Previous works \cite{7780635} decompose the images into patches then fit those discriminative and non discriminative patches to a CNN one by one or resize to a lower resolution. We resize to an appropriate resolution (not necessarily lower for CNN) then use all patches of each image at once with ViT. Given an image $X^{W \times H \times C}$ with spatial resolution ${W \times H}$, ViT firstly divides it into $N=\frac{WH}{P^2}$ patches where $P$ is the patch size. This leads to each spatial dimension being a multiple of patch size. However, WSI do not always come in such manner. To deal with the design choice we propose to use rectangular patch size and also use padding strategy in case the sizes do not match. Although padding may have small effect on classification results, it is important for WSI segmentation. The new number of patches can be computed as in \ref{npatch}:
\begin{equation}
    N= \left\lceil\frac{H}{P_1}\right\rceil \cdot \left\lceil\frac{W}{P_2}\right\rceil,
    \label{npatch}
\end{equation}
where $P_1$ and $P_2$ are the spatial dimensions of a patch. Figure \ref{fig:cls} depicts the proposed architecture for cancer WSI classification.

\subsection{Segmentation}
\begin{figure}[h]
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=0.8\linewidth]{media/prev.png} 
\caption{Previous patch-based approach}
\label{fig:prev}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=0.8\linewidth]{media/prop.png}
\caption{Proposed segmentation architecture}
\label{fig:prop}
\end{subfigure}

\caption{WSI segmentation model diagram}
\label{fig:seg}
\end{figure}

If the image is too large we divide it into chunks of appropriate size then use those chunk as original image. Doing so we reduce the number on chunks to be treated sequentially compared to existing approaches which will produce large number of chunks then treats them sequentially \ref{fig:prev}. Most existing biomedical images segmentation approaches integrate UNet\cite{ronneberger2015unet} or a large CNN architecture. Our method also have the advantage to allow the insertion of part of an UNet module at the output of the transformer if needed.
Figure \ref{fig:prop} depicts the proposed segmentation approach. The model can produce a sequence of images at once if the ground true is a sequence of images like in machine translation. Also, we can bypass the post processing part and produce accurate segmentation mask. The reconstruction head in the Figure \ref{fig:prop} can be a set of convolution layers to produce the appropriate final shape for the output model.

\subsection{Evaluation metric}
To evaluate the proposed method, we use two different metrics for prediction and segmentation. The prediction level metric consists of: \textit{F1}, \textit{precision}, and the \textit{sensitivity} as defined in \ref{metric1}

\begin{equation}
\begin{split}
   \text{F1} & = \frac{2TP}{2TP+FP+ FN}, \\
   \text{Sensitivity} & = \frac{TP}{TP+FN}, \\
   \text{Precision} & = \frac{TP}{TP+FP} ,
   \label{metric1}
\end{split}
\end{equation}
where $TP$, $FP$ and $FN$ are true positive, false positive and false negative, respectively.
For segmentation level metric, the intersection of Union metric: Jacard index or DICE's coefficient $D$ defined in equation \ref{metric2},
\begin{equation}
    D(\hat{Y},Y)=2\frac{|\hat{Y} \cap Y|}{|\hat{Y} \cup Y|},
    \label{metric2}
\end{equation}
where $\hat{Y}$ and $Y$ are the predicted region from the model and the ground truth region of input image, respectively.

\section{Preliminary experiments}
At this stage of our work we evaluate the proposed model on breast cancer data compared to some recent works. The proposed classifier was trained using an RTX2080ti and 4 RTX TitanX GPUs  with TensorFlow and PyTorch library. Most of the training was done on RTX2080ti desktop.
\subsection{Data}
Breast Cancer Histopathological Image Classification (BreakHis) dataset \cite{BENHAMMOU20209} was used to assess the performance. This dataset is composed of 9,109 microscopic images of breast tumor tissue collected from 82 patients using different magnifying factors (40X, 100X, 200X, and 400X). It contains 2,480  benign and 5,429 malignant samples ($700\times 450$ pixels, 3-channel RGB, 8-bit depth in each channel, PNG format). Benign and malignant subtypes \ref{TAB1} are also provided which makes this dataset an good choice for comparing models performance. According to the dataset, there are four histological distinct types of benign breast tumors (B): adenosis (A), fibroadenoma (F), phyllodes tumor (PT), and tubular adenona (TA) and four malignant breast tumors (M): carcinoma (DC), lobular carcinoma (LC), mucinous carcinoma (MC) and papillary carcinoma (PC).

\begin{table}[ht]
\centering
\resizebox{\columnwidth}{!}{\begin{tabular}{c|c|cccc|c|c} %{llllllll}
\toprule
\multirow{2}{*}{Class} & \multirow{2}{*}{Type} & \multicolumn{4}{c|}{Magnification} & \multirow{2}{*}{Total} & \multirow{2}{*}{Sum} \\
& & 40X & 100X & 200X & 400X & & \\ \midrule
\multirow{4}{*}{B} & A & 114  & 113  & 111  & 106 & 444 & \multirow{4}{*}{2480}  \\
 & F  & 253  & 260  & 264  & 237 & 1014 & \\
 & TA & 109 & 121  & 108  & 115 & 453 & \\
 & PT & 149  & 150  & 140  & 130 & 569 & \\ \midrule
\multirow{4}{*}{M} & DC & 864  & 903  & 896  & 788 & 3451  & \multirow{4}{*}{5429}  \\
 & LC & 156  & 170  & 163  & 137  & 626 & \\
 & MC & 205  & 222  & 196  & 169 & 792 & \\
 & PC & 145  & 142  & 135  & 138 & 560 &  \\ \midrule
\multicolumn{2}{c|}{Total} & 1995 & 2081 & 2013 & 1820 & 7909 & 7909\\
\bottomrule
\end{tabular}}
\caption{BreakHis dataset description}
\label{TAB1}
\end{table}

% \begin{table}[ht]
% \centering
% \begin{tabular}{c|c|cccc|c|c} %{llllllll}
% \hline
% \multirow{2}{*}{Class}   & \multirow{2}{*}{Type } & \multicolumn{4}{l|}{Magnification} & \multirow{2}{*}{Total} & \multirow{2}{*}{Sum}    \\
%                           &   & 40X  & 100X & 200X & 400X & & \\
%                           \hline
% \multirow{4}{*}{  B } & A & 114  & 113  & 111  & 106 & 444 & \multirow{4}{*}{2,480}  \\
%                           & F  & 253  & 260  & 264  & 237 & 1014 & \\
%                           & TA & 109 & 121  & 108  & 115 & 453 & \\
%                           & PT & 149  & 150  & 140  & 130 & 569 & \\
%                           \hline
% \multirow{4}{*}{M} & DC & 864  & 903  & 896  & 788 & 3451  & \multirow{4}{*}{5,429}  \\
%                           & LC & 156  & 170  & 163  & 137  & 626 & \\
%                           & MC & 205  & 222  & 196  & 169 & 792 & \\
%                           & PC & 145  & 142  & 135  & 138 & 560 &  \\
%                           \hline
% \multicolumn{2}{|l|}{Total}& 1995 & 2081 & 2013 & 1820 & 7909 & 7,909\\
% \hline
% \end{tabularx}
% \caption{BreaKHis dataset description}
% \label{TAB1}
% \end{table}

\subsection{Breast cancer classification using BreakHis dataset}
We consider two approaches to evaluate our model which are magnification specific binary(MSB) classification  and  multi classes classification. For the binary classification, we only consider benign and malignant to be the classes. For multi classes classification, we only consider the subclasses. The results of the experiment for binary classification are showed in Table \ref{result1}. In this experiment, for fair comparison we consider two state-of-the-art methods\cite{Xie2019,8353225} With similar setting on the same dataset.  Data augmentation techniques  consisting to increase the number of samples where not used. Also, we do not use any pretrained techniques.

\begin{table}[ht]
\centering
\resizebox{\columnwidth}{!}{\begin{tabular}{cc|cccc|c}
\toprule
\multirow{2}{*}{Works} & \multirow{2}{*}{Year} & \multicolumn{4}{c|}{Magnification} & \multirow{2}{*}{Mean} \\
 & & 40X & 100X & 200X & 400X & \\ \midrule
\cite{Xie2019} & '19 & 97.90 & 96.88 & 96.88 & 96.88 & 97.13 \\
Ours & '21 & \textbf{98.36} & 96.19 & 95.86 & \textbf{97.98} & 97.10 \\
VGG\cite{8353225} & '18 & 96.82 & 96.96 & 96.36 & 95.97 & 96.52 \\
Ens\cite{8353225} & '18 & 98.33 & \textbf{97.12} & \textbf{97.85} & 96.15 & \textbf{97.36} \\
\bottomrule
\end{tabular}}
\caption{Comparison of MSB classification results. VGG stands for VGG-16 architecture and Ens stands for Ensemble method proposed in \cite{8353225}. Boldface means the maximum within the respective column.}
\label{result1}
\end{table}

In this preliminary experiment we trained the proposed model from scratch. For comparison, the BreakHis dataset is randomly split into 70\% for training and 30\% for testing. We only applied horizontal flip and normalization. All methods are within in the same range although those method used complex convolution architectures. Based on the results presented in \cite{BENHAMMOU20209}, our approach achieves competitive compared to existing breast cancer classification method tested on BreakHis. However, further improvement are still needed. Therefore, we will perform further experiments, parameter tuning to outperform the state-of-the-art on BreakHis and also move to tissues segmentation. The results presented in this paper are preliminary results and the final results may different significantly. Therefore we have not yet include the evaluation metrics results.

\subsection{Additional experiments with pretrained ViT}
Some additional experiments were conducted with publicly available pretrained ViT model. This was to investigate the effect of pretraining on a drastically different image domains to lay basis for further investigation. For this model, the image was resized to 224-by-224 for preliminary experiment. However, this part will be modified in the coming end-to-end implementation. For experiment, a base model with patch size 16 and input size 224 was used. The experiments can be viewed \href{https://wandb.ai/jkgrad/vit-domain-adapt?workspace=user-jkgrad}{here}.

The results are provided Table \ref{result2}. As expected, it was found that pretrained models can absolutely leverage information obtained during pretraining. Even without data augmentation, the model already achieves the state-of-the-art result. When coupled with data augmentation, the model performance increases at low magnification, leading to the mean accuracy across magnifications levels of 98.52, which is remarkable. The effect of higher input resolution for downstream task, however, still needs to be investigated.

\begin{table}[ht]
\centering
\resizebox{\columnwidth}{!}{\begin{tabular}{c|cccc|c}
\toprule
\multirow{2}{*}{Works} & \multicolumn{4}{c|}{Magnification} & \multirow{2}{*}{Mean} \\
 & 40X & 100X & 200X & 400X & \\ \midrule
PT    & 97.66 & \textbf{98.72} & \textbf{98.01} & \textbf{98.35} & 98.19 \\
PT+AG & \textbf{99.00} & \textbf{98.72} & \textbf{98.01} & \textbf{98.35} & \textbf{98.52} \\
\bottomrule
\end{tabular}}
\caption{Experiments on pretraining. All models were trained under the same hyperparameters. PT stands for pretraining and AG stands for augmentation.}
\label{result2}
\end{table}

\section{Conclusion}
In this stage of work  we proposed a classification model for histological images using ViT architecture. The proposed method is fast to train and achieved good performance compared to previous works. In the coming stage, we will evaluate the model performance using the proposed metrics. Also, we will conduct more classification experiments to include the multi classes classification results. After that we will apply the proposed architecture for WSI segmentation. Finally we will investigate transfer learning and domain adaptation.

{\small
\bibliographystyle{ieee_fullname}
\bibliography{reference}
}

\end{document}

### 2021-04-25 code/crowdsourcing/download_from_s3.py
update crowdsourcing downloadscript-add annotations

@@ -11,6 +11,7 @@ BUCKET_NAME = "ai604"
 PREFIXS = [
     "dataset/images/",
     "dataset/masks/",
+    "dataset/annotations/",
     "dataset/meta/"
 ]
 

### 2021-05-09 paper/rebuttal/02_rebuttal.tex
Added rebuttal.

\documentclass[rebuttal]{cvpr}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}

% Include other packages here, before hyperref.
\usepackage{multirow, multicol, booktabs}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx}

\newcommand{\todoc}[2]{{\textcolor{#1} {\textbf{[#2]}}}}
\newcommand{\todored}[1]{\todoc{red}{\textbf{#1}}}
\newcommand{\TA}[1]{\todored{TA: #1}}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{0000} % Do not enter team number here
%\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\def\cvprPaperID{0000} % Do not enter team number here
\def\confYear{AI604 2021 spring}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{AI604 term project rebuttal / author response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
% \section{Introduction}

% After receiving paper reviews, authors should submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.

% Note that the author rebuttal is not visible to the reviewers. In other words, only TAs and the professor will read the rebuttal.

% \subsection{Response length}

% Author responses must be no longer than 1 page in length except for \textbf{References} and \textbf{Additional question}.

% \subsection{Note}

% Feel free to write the author response, and we recommend you not to spend your time so much on this. We aim to provide you a chance to improve your work by answering to the reviews. Each team will receive five or six reviews.

% \TA{Remove guidelines (Section 1) and write your response.}

%-------------------------------------------------------------------------
%\newpage

\section{Additional question}
% Each team should answer the below questions for evaluating their reviewers.

\subsection{Question 1}
\begin{itemize}
    % 리뷰어 1 2 3 4 5 6 은 우리의 프로젝트 내용을 이해했다.
    \item The reviewer 1 understood our main idea and contributions. \textbf{Yes}

    \item The reviewer 2 understood our main idea and contributions. \textbf{Yes}

    \item The reviewer 3 understood our main idea and contributions. \textbf{Yes}

    \item The reviewer 4 understood our main idea and contributions. \textbf{Yes}
    \item The reviewer 5 understood our main idea and contributions. \textbf{Yes}

    \item The reviewer 6 understood our main idea and contributions. \textbf{Yes}
\end{itemize}

\subsection{Question 2}
\begin{itemize}
    % 리뷰어 1 2 3 4 5 6 은 우리에게 건설적인 피드백을 제공했다.
    \item The reviewer 1 provided constructive feedback or advice. \textbf{No}, no suggestion was given.

    \item The reviewer 2 provided constructive feedback or advice.
    \textbf{No}, no suggestion was given.

    \item The reviewer 3 provided constructive feedback or advice. \textbf{Yes}, we will include computation costs and GPU memory comparison experiments in our following reports. The reviewer also suggested including Transformer architecture diagram, but we shall decide according to the length of the final version of the paper. We made changes to the diagrams to make it clearer (Figure \ref{fig:seg+class} \ref{fig:class} \ref{fig:seg} ). We will be providing better explanations for the training procedure in the upcoming versions.

    \item The reviewer 4 provided constructive feedback or advice. \textbf{Yes}, the explanations on how the segmentation reconstruction head works will be provided in the later versions. Our approach will be mostly convolution-free (mathematical operation-wise), and we are still investigating various methods for reconstruction. The experiment setup will be further organized and released accordingly. Note that the experiments provided in the progress report were only preliminary, and more experiments may be conducted with different settings.

    \item The reviewer 5 provided constructive feedback or advice. \textbf{Yes}, the reviewer asked some questions. For the first question, pixel-by-pixel accuracy is sometimes used as evaluation metric in segmentation tasks. It is often provided as 
    \[ \text{Acc} := \frac{TP + TN}{TP + TN + FP + FN} \]
    However, intersection-over-union (IoU) or other metrics designed for segmentation are often preferred because pixel-by-pixel accuracy can provide misleading results when the class representation is small within the image. This is because the measure can be biased in reporting how well the model identify non-present class. In our particular dataset, there are some small regions in the image, which can lead to misleading metrics.

    For the second question, domain adaptation and transfer learning are often used interchangeably in computer vision literature. Even though it is not entirely correct, but we follow through with the general academic consensus. In our case with medical image tasks, domain adaptation can be helpful in a case where the model needs to be adopted in different hospitals. The model is expected to perform equally well with semantically similar but distributional different images, which is often the case in real-life circumstances.

    \item The reviewer 6 provided constructive feedback or advice. \textbf{Neutral}. The author suggests some different variants of ViT such as DeiT and CaiT. Some of these model setups are already being investigated for the upcoming progress report. The author also says a large private dataset is needed for training ViT, but we have already observed nice performance in some of the preliminary experiments with both pretrained and non-pretrained models. We also plan to experiment with the recently proposed MLP Mixer, convolution- and attention-free model for images. 
\end{itemize}

\subsection{Question 3}
Redrawn figures in response to Reviewer 3 are provided below:

    \begin{figure}[ht]
    \begin{center}
       \includegraphics[width=0.8\linewidth]{media/Blockdiagram.png}
    \end{center}
       \caption{Block diagram of the model for WSIs segmentation and classification}
    \label{fig:seg+class}
    \end{figure}

    \begin{figure}[ht]
    \begin{center}
       \includegraphics[width=0.8\linewidth]{media/classifier.png}
    \end{center}
       \caption{Block diagram of the model for WSIs classification}
    \label{fig:class}
    \end{figure}

    \begin{figure}[ht]
        \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=0.8\linewidth]{media/previous-patch-based-approach.png}
            \caption{Previous patch-based approach}
            \label{fig:prev}
        \end{subfigure}
        \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=0.8\linewidth]{media/proposed-seg.png}
            \caption{Proposed segmentation architecture}
            \label{fig:prop}
        \end{subfigure}
        \caption{WSI segmentation model diagram}
        \label{fig:seg}
    \end{figure}

% {\small
% \bibliographystyle{ieee_fullname}
% \bibliography{reference}
% }

\end{document}

### 2021-05-11 code/crowdsourcing/crowdsourcing_preprocess.py
preprocess code for padding & dividing img

@@ -1,0 +1,78 @@
+#!/usr/bin/env python3
+import cv2
+import numpy as np
+import os
+
+from PIL import Image
+from torchvision.transforms.functional import pad
+from typing import Tuple
+
+IMAGES_PATH = "dataset/images"  # Original Images Folder
+MASKS_PATH = "dataset/masks"  # Original Masks Folder
+IMAGE_PATCHES = "dataset/patches/images"  # Destination (Images)
+MASK_PATCHES = "dataset/patches/masks"  # Destination (Masks)
+PATCH_SIZE = 1024
+
+
+def create_folder(foldername: str):
+    """Create folder to store patches"""
+    if not os.path.isdir(foldername):
+        os.makedirs(foldername)
+
+
+def compute_pixel_diff(ori_size: int, patch_size: int = 1024) -> int:
+    """Compute pixel different for padding purpose"""
+    return patch_size - (ori_size % patch_size)
+
+
+def compute_padding_size(pixels: int) -> Tuple[int, int]:
+    """Compute padding size for each side (left, right) or (top, bottom)"""
+    pad_size = pixels // 2
+    return (pad_size, pad_size) if (pixels % 2 == 0) else (pad_size, pad_size + 1)
+
+
+def get_padding(img: np.ndarray, patch_size: int = 1024) -> Tuple[int, int, int, int]:
+    """Get padding size for four sides"""
+    diff_height = compute_pixel_diff(img.shape[0], patch_size)
+    diff_width = compute_pixel_diff(img.shape[1], patch_size)
+    horizontal_pad = compute_padding_size(diff_height)
+    vertical_pad = compute_padding_size(diff_width)
+    return (vertical_pad[0], horizontal_pad[0], vertical_pad[1], horizontal_pad[1])
+
+
+def pad_image(img: np.ndarray, patch_size: int = 1024) -> np.ndarray:
+    """Pad image/ mask according to padding size"""
+    padding = get_padding(img, patch_size)
+    return np.array(pad(Image.fromarray(img), padding))
+
+
+def generate_image_patches(img: np.ndarray, patch_size: int = 1024):
+    """Generate patches for each original image/ mask"""
+    for y in range(0, img.shape[0], patch_size):
+        y_end = y + patch_size
+        for x in range(0, img.shape[1], patch_size):
+            x_end = x + patch_size
+            yield img[y:y_end, x:x_end]
+
+
+if __name__ == "__main__":
[…]

### 2021-05-12 paper/rebuttal-1/00_main.tex
Changed folder name

% \documentclass[review]{cvpr}
\documentclass[final]{cvpr}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
% \setcounter{page}{4321} % For final version only

\begin{document}

%%%%%%%%% TITLE
\title{AI604 term project paper template}

\author{Except for the proposal, do not provide student information (e.g., name and student ID)
}

\maketitle

\begin{abstract}
Abstract is optional. This will not affect the final score.
\end{abstract}

\section{Guideline: Proposal}

Feel free to describe your idea. We expect that the proposal includes \textit{the definition of the task}, \textit{dataset}, and \textit{tentative plan for the project}.

Please note that you can change the project topic after the proposal. However, we strongly discourage you from changing the topic after progress 1.

\section{Guideline: Progress 1 / 2}

After the proposal, we will check the progress of your project two times. You should submit the progress reports, and the reports should contain the contents of the proposal, \textit{related work} (and \textit{previous work} if exist), \textit{method}, and \textit{experiment}. It is okay to omit the result.

Other students will review your progress reports, and it is in a fully \textit{double-blind} manner. Each team will receive three or four reviews, and the review scores will affect your final score. For fair evaluation, students who have the same advisor do not review each others' work, and also \textbf{you will judge the reviews' review!} In the case of Progress 1, every team should submit \textit{author response}. The length of the response is up to one page. We provide the template for the author response; please check \texttt{02\_rebuttal.tex}.

\section{Guideline: Final}

The final report should contain the contents of the proposal and the progress reports, \textit{result}, and \textit{etc}. The length of the paper is up to nine pages except for \textit{reference}. Reference is optional, but we strongly recommend you to add the reference.

There will be a project presentation session at the end of the semester. Further instructions will be announced later.

\section{Etc}

If you have a question, send us an e-mail or a message to the Kakao open chat room.

{\small
\bibliographystyle{ieee_fullname}
\bibliography{reference}
}

\end{document}

### 2021-05-12 paper/rebuttal-1/01_review.tex
Changed folder name

% \documentclass[review]{cvpr}
\documentclass[final]{cvpr}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\newcommand{\todoc}[2]{{\textcolor{#1} {\textbf{[#2]}}}}
\newcommand{\todored}[1]{\todoc{red}{\textbf{#1}}}
\newcommand{\TA}[1]{\todored{TA: #1}}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
% \setcounter{page}{4321} % For final version only

\begin{document}

%%%%%%%%% TITLE
\title{AI604 term project review for submission \TA{Paper ID})}

\author{Reviewer ID: \TA{Reviewer ID}
}

\maketitle

\section{Guideline: Review}

As we announced before, all students should review other teams' papers. For convenience, we have prepared three questions, and you can write reviews by answering them. Each student will review three papers, and \textbf{each review must be submitted in separate files}. \TA{Remove this guideline.}

\section{Questions}

We expect insightful reviews! Keep in mind that \textbf{the authors of the paper will evaluate your review, and this will be reflected in your final score.}

\subsection{Please provide the summary of the paper (less than 100 words).}

\TA{summary...}

\subsection{Suggestions for the paper (less than 150 words).}

\TA{suggestion...}

\subsection{Final score and detailed comments (less than 150 words).}

\TA{detailed comments...}

% 각 리뷰어는 본인이 리뷰하는 세 논문에 대해 총 12점을 주어야 합니다. 예를 들어 두 개의 논문에 각각 5점을 주었다면, 남은 하나의 논문에는 2점을 주어야 합니다. 이는 어뷰징 (e.g., 논문 모두에 최저점을 주는 행위) 을 방지하기 위한 것으로, 조교가 꼼꼼하게 확인할 예정입니다.
\textbf{IMPORTANT RULE:} You should give a total of 12 points for the three papers you review. For example, if you gave five points to two papers, you should give two points to the remaining one. This rule is a way to prevent abusing (e.g., giving the lowest point for all papers), and TAs will check it strictly.

\TA{Final score: (1/2/3/4/5). -- higher is better}

\section{Etc}

If you have a question, send us an e-mail or a message to the Kakao open chat room.

% {\small
% \bibliographystyle{ieee_fullname}
% \bibliography{reference}
% }

\end{document}

### 2021-05-12 code/train/classify.py

@@ -186,7 +186,7 @@ def main():
     # Set random seed for reproducibility
     set_seed(args.seed)
 
-    # Accelerator (syntatic sugar for distributed / fp16 training)
+    # Accelerator (syntactic sugar for distributed / fp16 training)
     accelerator = Accelerator(fp16=args.amp, cpu=True if args.device=='cpu' else False)
 
     # Compute input size based on image size and patch size

### 2021-05-22 code/crowdsourcing/utils_cs.py
add dice func

@@ -12,6 +12,7 @@ def mIoU(pred_mask, mask, smooth=1e-10, n_classes=22):
         mask = mask.contiguous().view(-1)
 
         iou_per_class = []
+        dice_per_class = []
         for clas in range(0, n_classes):  # loop per pixel class
             true_class = pred_mask == clas
             true_label = mask == clas
@@ -25,8 +26,10 @@ def mIoU(pred_mask, mask, smooth=1e-10, n_classes=22):
                 union = torch.logical_or(true_class, true_label).sum().float().item()
 
                 iou = (intersect + smooth) / (union + smooth)
+                dice = (2 * intersect + smooth) / (union + smooth)
                 iou_per_class.append(iou)
-        return np.nanmean(iou_per_class)
+                dice_per_class.append(dice)
+        return np.nanmean(iou_per_class), np.nanmean(dice_per_class)
 
 
 def pixel_accuracy(output, mask):

### 2021-05-23 code/crowdsourcing/vitseg.py
Add files via upload

@@ -1,0 +1,295 @@
+import os
+import numpy as np
+import pandas as pd
+from glob import glob
+# import cv2
+from PIL import Image
+# import matplotlib.pyplot as plt
+from tqdm import tqdm
+
+
+import torch
+import torchvision
+import torchvision.transforms as transforms
+import torch.nn.functional as F
+
+from torch import nn, einsum
+from einops import rearrange, repeat
+from einops.layers.torch import Rearrange
+
+from sklearn.model_selection import train_test_split
+from torch.optim.lr_scheduler import StepLR
+from torch.utils.data import DataLoader, Dataset
+from torchvision import datasets
+import torch.optim as optim
+os.environ["CUDA_VISIBLE_DEVICES"] = '0'
+
+class CancerDataset(Dataset):
+
+    def __init__(self, image_dir, mask_dir, transform=None):
+        super(CancerDataset, self).__init__()
+        self.image_dir = image_dir
+        self.image_files = os.listdir(image_dir)
+        self.mask_dir = mask_dir
+        self.transform = transform
+
+    def __len__(self):
+        return len(self.image_files)
+
+    def __getitem__(self, index):
+        image_file = self.image_files[index]
+        mask_file = self.image_files[index]
+        image_path = os.path.join(self.image_dir, image_file)
+        mask_path = os.path.join(self.mask_dir, mask_file)
+        image = Image.open(image_path).convert('RGB')
+        #         image = np.array(image)
+        mask = Image.open(mask_path)
+        mask = np.array(mask)
+        if self.transform:
+            image = self.transform(image)
+
+        label = torch.Tensor(mask).long()
+        return image, label
+
+
+
+
+class Reshape(nn.Module):
+    def __init__(self, mask_size=1024,num_classes=22):
+        super(Reshape, self).__init__()
+        self.mask = mask_size
+        self.num_classes= num_classes
+
+    def forward(self, x):
+        return x.view(-1,self.num_classes,self.mask,self.mask)
+
+class PreNorm(nn.Module):
+    def __init__(self, dim, fn):
+        super().__init__()
+        self.norm = nn.LayerNorm(dim)
+        self.fn = fn
+    def forward(self, x, **kwargs):
+        return self.fn(self.norm(x), **kwargs)
+
[…]

### 2021-05-23 code/crowdsourcing/utils_cs.py
cleanup utils_cs.py

@@ -1,7 +1,8 @@
 import numpy as np
-import torch
+import torch # torch >= 1.7.1
 import torch.nn.functional as F
 from torchvision import transforms as T
+from tqdm import tqdm
 
 
 def mIoU(pred_mask, mask, smooth=1e-10, n_classes=22):
@@ -39,8 +40,6 @@ def pixel_accuracy(output, mask):
         accuracy = float(correct.sum()) / float(correct.numel())
     return accuracy
 
-def test_fun(d=0):
-    print(d)
 
 def predict_image_mask_miou(
     model,
@@ -48,7 +47,7 @@ def predict_image_mask_miou(
     mask,
     mean=[0.60258, 0.44218, 0.57057],
     std=[0.30052, 0.27571, 0.27647],
-    device=torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+    device=torch.device("cuda" if torch.cuda.is_available() else "cpu"),
 ):
     model.eval()
     t = T.Compose([T.ToTensor(), T.Normalize(mean, std)])
@@ -74,7 +73,7 @@ def predict_image_mask_pixel(
     mask,
     mean=[0.60258, 0.44218, 0.57057],
     std=[0.30052, 0.27571, 0.27647],
-    device=torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+    device=torch.device("cuda" if torch.cuda.is_available() else "cpu"),
 ):
     model.eval()
     t = T.Compose([T.ToTensor(), T.Normalize(mean, std)])
@@ -98,7 +97,7 @@ def miou_score(model, test_set):
     score_iou = []
     for i in tqdm(range(len(test_set))):
         img, mask = test_set[i]
-        pred_mask, score = predict_image_mask_miou(model, img, mask)
+        _, score = predict_image_mask_miou(model, img, mask)
         score_iou.append(score)
     return score_iou
 
@@ -107,6 +106,6 @@ def pixel_acc(model, test_set):
     accuracy = []
     for i in tqdm(range(len(test_set))):
         img, mask = test_set[i]
-        pred_mask, acc = predict_image_mask_pixel(model, img, mask)
+        _, acc = predict_image_mask_pixel(model, img, mask)
         accuracy.append(acc)
     return accuracy

### 2021-05-25 paper/progress-2/00_main.tex
Added dirty code for convolution free method.

--- 2021-04-25 paper/progress-1/00_main.tex
@@
 \\
-\textbf{Vision Transformer} Vision Transformer (ViT)\cite{dosovitskiy2020image} closely adapts Transformer Architecture for natural language processing for image classification.
-The concept consists of dividing the whole image into small chunks analogous to the sequence of tokens in machine translation.
+\textbf{Vision Transformer} Vision Transformer (ViT)\cite{dosovitskiy2020image} closely adapts Transformer Architecture from natural language processing for image classification.
+The concept consists of dividing the whole image into small chunks analogous to the sequence of language tokens.
 There are a few modifications from the original Transformer architecture for image domains:
@@
 %     \centering
-% \resizebox{\columnwidth}{!}{\begin{tabular}{c|c|c|c}
+%     \begin{tabular}{cccc}
 %         \toprule
-% Network & Salient Feature & Parameters & FLOP \\ \toprule
-% AlexNet &  Deep & 61M & 1.5B \\ 
-% VGG-16 & Fixed-size kernels & 138M & 19.6B \\
-% Inception & Wide/parallel kernels & 43M & 2B \\
-% ResNet-152 & Skip connection & 60M & 11B \\
-% ViT & Transformer & 86M & \\
-% \bottomrule
-% \end{tabular}}
-% \caption{Comparing number of trainable parameters and FLOPs according to model architectures. M stands for million and B billion.}
-% \label{param}
+%         Models & Image size & \# Params & FLOPs  \\ \midrule
+%         \multicolumn{4}{c}{Convolution} \\ \midrule
+%         Resnet-101 & $224^2$ & 45M & \\
+%         EffNet-B3 & $300^2$ & 12M & 1.8G \\
+%         EffNet-B4 & $380^2$ & 19M & 4.2G \\ \midrule
+%         \multicolumn{4}{c}{Transformers} \\ \midrule
+%         ViT-B/16 & $384^2$ & 86M & 55.4G \\
+%         ViT-L/16 & $384^2$ & 307M & 190.7G \\
+%         DeiT-B   & $224^2$ & 22M & 4.6G \\
+%         DeiT-B   & $384^2$ & 86M & 17.5G \\ \bottomrule
+%     \end{tabular}
+%     \caption{Computation and parameter comparison of different image model backbones on ImageNet. The table was adapted from \cite{touvron2021training}.}
+%     \label{computation_comparison}
 % \end{table}
@@
 % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   \includegraphics[width=0.8\linewidth]{media/roi1.PNG}
+   \includegraphics[width=0.8\linewidth]{media/roi1-new.png}
 \end{center}
@@
 % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   \includegraphics[width=0.8\linewidth]{media/classify.png}
+   \includegraphics[width=0.8\linewidth]{media/classify-new.png}
 \end{center}
@@
 We resize to an appropriate resolution (not necessarily lower for CNN) then use all patches of each image at once with ViT.
-Given an image $X^{W \times H \times C}$ with spatial resolution ${W \times H}$, ViT firstly divides it into $N=\frac{WH}{P^2}$ patches where $P$ is the patch size.
+Given an image $X^{H \times W \times C}$ with spatial resolution ${H \times W}$, ViT firstly divides it into $N = \frac{HW}{P^2}$ patches where $P$ is the patch size.
 This leads to each spatial dimension being a multiple of patch size.
@@
 \begin{figure}[h]
+    \centering
     \begin{subfigure}{0.5\textwidth}
-\includegraphics[width=0.8\linewidth]{media/prev.png} 
+        \centering
+        \resizebox{0.8\columnwidth}{!}{\includegraphics[width=0.8\linewidth]{media/prev-new.png}}
         \caption{Previous patch-based approach}
@@
     \begin{subfigure}{0.5\textwidth}
-\includegraphics[width=0.8\linewidth]{media/prop.png}
+        \centering
+        \resizebox{0.8\columnwidth}{!}{\includegraphics[width=0.8\linewidth]{media/prop-new.png}}
         \caption{Proposed segmentation architecture}
@@
     \end{subfigure}
-
 \caption{WSI segmentation model diagram}
@@
 Doing so we reduce the number on chunks to be treated sequentially compared to existing approaches which will produce large number of chunks then treats them sequentially \ref{fig:prev}.
-Most existing biomedical images segmentation approaches integrate UNet\cite{ronneberger2015unet} or a large CNN architecture.
+Most existing biomedical images segmentation approaches integrate UNet\cite{ronneberger2015unet} or a large CNN backbone that can only take fixed input sizes.
 Our method also have the advantage to allow the insertion of part of an UNet module at the output of the transformer if needed.
+
 Figure \ref{fig:prop} depicts the proposed segmentation approach.
@@
 The reconstruction head in the Figure \ref{fig:prop} can be a set of convolution layers to produce the appropriate final shape for the output model.
+\\
+The input image to our segmentation network is a 2D image of size $(H \times W \times C)$ where $H=W$ are the image height and width, and $C$ the number of channels (3 for RGB images).
+
+The input image is then partitioned to a sequence of patches of size $(P\times P\times C)$.
+These patches are passed through the transformer which outputs the embedding matrix of shape $(B, N, d)$,  where $B$ is the batch size, $N$ the number of patches and $d$ the embedding dimension.
+For reconstructing the prediction mask, we can add a multi-layer perceptron to transform that embedding into a matrix of shape $(B, cHW)$ and reshape to $(B, c, H, W)$ where $c$ is the number of classes.
+Such an approach requires a lot of memory resources for large images.
+Another way to reconstruct the segmentation mask is to directly reshape the embedding matrix into $(B, N, d_1, d_2)$ where $d = d_1\times d_2$, then apply transpose convolution as in UNet architecture.
+This approaches reduces largely the numbers of convolution layers while playing the role of the encoder in UNet-like architecture.
 
 \subsection{Evaluation metric}
-To evaluate the proposed method, we use two different metrics for prediction and segmentation.
-The prediction level metric consists of: \textit{F1}, \textit{precision}, and the \textit{sensitivity} as defined in \ref{metric1}
+To evaluate the proposed method, we use the following metrics for each tasks.
 
+\subsubsection{Classification}
+\begin{enumerate}
+    \item[\textbullet] Accuracy: a naive multi-class classification metric. 
+    \item[\textbullet] F-1 score: given TP, FP, and FN are true positive, false positive, and false negative, F-1 score can be computed as 
     \begin{equation}
-\begin{split}
-   \text{F1} & = \frac{2TP}{2TP+FP+ FN}, \\
-   \text{Sensitivity} & = \frac{TP}{TP+FN}, \\
-   \text{Precision} & = \frac{TP}{TP+FP} ,
-   \label{metric1}
-\end{split}
+         \text{F-1} = \frac{2\text{TP}}{2\text{TP}+\text{FP}+ \text{FN}}
+         \label{f1-metric}
     \end{equation}
-where $TP$, $FP$ and $FN$ are true positive, false positive and false negative, respectively.
-For segmentation level metric, the intersection of Union metric: Jacard index or DICE's coefficient $D$ defined in equation \ref{metric2},
+\end{enumerate}
+
+\subsubsection{Segmentation}
+\begin{enumerate}
+    \item[\textbullet] Pixel accuracy: a naive pixel-wise accuracy metric. 
+    \item[\textbullet] Intersection over Union (IoU/Jaccard): IoU, also known as Jaccard index, can be computed in a similar manner to \ref{f1-metric}, but without the constant:
     \begin{equation}
-    D(\hat{Y},Y)=2\frac{|\hat{Y} \cap Y|}{|\hat{Y} \cup Y|},
-    \label{metric2}
+        \text{Dice} = \frac{\text{TP}}{\text{TP}+\text{FP}+ \text{FN}}
+        \label{dice-score-metric}
     \end{equation}
-where $\hat{Y}$ and $Y$ are the predicted region from the model and the ground truth region of input image, respectively.
+    \item[\textbullet] Dice coefficient (Dice/F-1): Dice coefficient is defined to be the following where $\hat{Y}$ and $Y$ are the predicted region from the model and the ground truth region of input image.
+    \begin{equation}
+        \text{Dice} (\hat{Y},Y)=2\frac{|\hat{Y} \cap Y|}{|\hat{Y} \cup Y|},
+        \label{dice-score}
+    \end{equation}
+    This is equivalent to F-1 score in the context of segmentation, which can be computed by \ref{f1-metric}.
+\end{enumerate}
 
-\section{Preliminary experiments}
-At this stage of our work we evaluate the proposed model on breast cancer data compared to some recent works.
-The proposed classifier was trained using an RTX2080ti and 4 RTX TitanX GPUs  with TensorFlow and PyTorch library.
-Most of the training was done on RTX2080ti desktop.
-\subsection{Data}
+% \begin{equation}
+% \begin{split}
+%   \text{F1} & = \frac{2\text{TP}}{2\text{TP}+\text{FP}+ \text{FN}}, \\
+%   \text{Sensitivity} & = \frac{TP}{TP+FN}, \\
+%   \text{Precision} & = \frac{TP}{TP+FP} ,
+%   \label{metric1}
+% \end{split}
+% \end{equation}
+
+\section{Experiments}
+\subsection{Classification}
+\subsubsection{Dataset description}
 Breast Cancer Histopathological Image Classification (BreakHis) dataset \cite{BENHAMMOU20209} was used to assess the performance.
@@
 
-% \begin{table}[ht]
-% \centering
-% \begin{tabular}{c|c|cccc|c|c} %{llllllll}
-% \hline
-% \multirow{2}{*}{Class}   & \multirow{2}{*}{Type } & \multicolumn{4}{l|}{Magnification} & \multirow{2}{*}{Total} & \multirow{2}{*}{Sum}    \\
-%                           &   & 40X  & 100X & 200X & 400X & & \\
-%                           \hline
-% \multirow{4}{*}{  B } & A & 114  & 113  & 111  & 106 & 444 & \multirow{4}{*}{2,480}  \\
-%                           & F  & 253  & 260  & 264  & 237 & 1014 & \\
-%                           & TA & 109 & 121  & 108  & 115 & 453 & \\
-%                           & PT & 149  & 150  & 140  & 130 & 569 & \\
-%                           \hline
-% \multirow{4}{*}{M} & DC & 864  & 903  & 896  & 788 & 3451  & \multirow{4}{*}{5,429}  \\
-%                           & LC & 156  & 170  & 163  & 137  & 626 & \\
-%                           & MC & 205  & 222  & 196  & 169 & 792 & \\
-%                           & PC & 145  & 142  & 135  & 138 & 560 &  \\
-%                           \hline
-% \multicolumn{2}{|l|}{Total}& 1995 & 2081 & 2013 & 1820 & 7909 & 7,909\\
-% \hline
-% \end{tabularx}
-% \caption{BreaKHis dataset description}
-% \label{TAB1}
-% \end{table}
-
-\subsection{Breast cancer classification using BreakHis dataset}
-We consider two approaches to evaluate our model which are magnification specific binary(MSB) classification  and  multi classes classification.
+\subsubsection{Experiment setup}
+We consider two approaches to evaluate our model which are magnification specific binary(MSB) classification  and  magnification specific multi classes classification (MSM).
 For the binary classification, we only consider benign and malignant to be the classes.
@@
 The results of the experiment for binary classification are showed in Table \ref{result1}.
-In this experiment, for fair comparison we consider two state-of-the-art methods\cite{Xie2019,8353225} With similar setting on the same dataset.
-Data augmentation techniques  consisting to increase the number of samples where not used.
-Also, we do not use any pretrained techniques.
+In this experiment, we consider two state-of-the-art methods \cite{Xie2019,8353225} on the same dataset.
+Data augmentation techniques were not used.
+Also, we do not use any pretrained models.
+
+We  train the model for both binary and multi-class classification in a multi-label classification manner.
+In this experiment we train the proposed model from scratch with patch size $(20 \times 50)$ and input size $(460\times 700 \times 3)$.
+For comparison, the BreakHis dataset is randomly split into 70\% for training and 30\% for testing for each magnification factor.
+We only consider the methods that preprocess the dataset in the same manner as we do.
+Table \ref{result0} presents the experimentation results.
+
+\subsubsection{Result}
+The model achieves good performance on the disease classes compared to the subclasses.
+However, the performance of the subclasses can be improved if they are trained separately.
+The performance on the subclasses is comparable to existing methods \cite{BENHAMMOU20209,Xie2019}.
+Based on the results presented in \cite{BENHAMMOU20209}, our approach achieves competitive results \ref{result1} compared to existing breast cancer classification method tested on BreakHis.
+However, further improvement are still needed for the multilabels classification.
+Therefore, we will perform further experiments with non combined training, parameter tuning to outperform the state-of-the-art on BreakHis and move to tissues segmentation.
+The results presented in this paper are preliminary results and the final results may different significantly.
+
+\begin{table}[ht]
+\centering
+\resizebox{\columnwidth}{!}{
+\begin{tabular}{|l|l|l|l|l|l|} 
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Classification\end{tabular}} & \multirow{2}{*}{criteria} & \multicolumn{4}{l|}{Magnification}  \\ 
+\cline{3-6} &  & 40X   & 100X  & 200X   & 400 \\ 
+\hline
+\multirow{3}{*}{MSB  } & F-1 micro & 99.00 & 98.00 & 100.00 & 99.00  \\ 
+\cline{2-6}& F-1 macro & 98.88 & 97.68 & 99.45  & 99.37\\ 
+\cline{2-6}& Acc. & 99.00 & 98.08 & 99.50  & 99.45 \\ 
+\hline
+\multirow{3}{*}{MSM} & F-1 micro & 89.00    & 90.00   & 90.00     &90.00 \\ 
+\cline{2-6} & F-1 macro & 87.10 & 86.99 &86.33    & 88.13         \\ 
+\cline{2-6} & Acc.  & 89.48  & 89.76    & 90.23    & 89.74 \\
+\hline
+\end{tabular}}
+\caption{Evaluation results on Breakhis dataset.}
+\label{result0}
+\end{table}
 
@@
 \cite{Xie2019} & '19 & 97.90 & 96.88 & 96.88 & 96.88 & 97.13 \\
-Ours & '21 & \textbf{98.36} & 96.19 & 95.86 & \textbf{97.98} & 97.10 \\
+Ours & '21 & \textbf{99.00} & \textbf{98.08} & \textbf{99.50} & \textbf{99.45} & \textbf{99.01} \\
 VGG\cite{8353225} & '18 & 96.82 & 96.96 & 96.36 & 95.97 & 96.52 \\
-Ens\cite{8353225} & '18 & 98.33 & \textbf{97.12} & \textbf{97.85} & 96.15 & \textbf{97.36} \\
+Ens\cite{8353225} & '18 & 98.33 & 97.12 & 97.85 & 96.15 & 97.36 \\
 \bottomrule
@@
 
-In this preliminary experiment we trained the proposed model from scratch.
-For comparison, the BreakHis dataset is randomly split into 70\% for training and 30\% for testing.
-We only applied horizontal flip and normalization.
-All methods are within in the same range although those method used complex convolution architectures.
-Based on the results presented in \cite{BENHAMMOU20209}, our approach achieves competitive compared to existing breast cancer classification method tested on BreakHis.
-However, further improvement are still needed.
-Therefore, we will perform further experiments, parameter tuning to outperform the state-of-the-art on BreakHis and also move to tissues segmentation.
-The results presented in this paper are preliminary results and the final results may different significantly.
-Therefore we have not yet include the evaluation metrics results.
-
-\subsection{Additional experiments with pretrained ViT}
-Some additional experiments were conducted with publicly available pretrained ViT model.
+% \subsection{Additional experiments with pretrained ViT}
+% Some additional experiments were conducted with publicly available pretrained ViT model.
 This was to investigate the effect of pretraining on a drastically different image domains to lay basis for further investigation.
@@
 
-The results are provided Table \ref{result2}.
+% The results are provided Table \ref{result2}.
 As expected, it was found that pretrained models can absolutely leverage information obtained during pretraining.
@@
 
+% \begin{table}[ht]
+% \centering
+% \resizebox{\columnwidth}{!}{\begin{tabular}{c|cccc|c}
+% \toprule
+% \multirow{2}{*}{Works} & \multicolumn{4}{c|}{Magnification} & \multirow{2}{*}{Mean} \\
+%  & 40X & 100X & 200X & 400X & \\ \midrule
+% PT    & 97.66 & \textbf{98.72} & \textbf{98.01} & \textbf{98.35} & 98.19 \\
+% PT+AG & \textbf{99.00} & \textbf{98.72} & \textbf{98.01} & \textbf{98.35} & \textbf{98.52} \\
+% \bottomrule
+% \end{tabular}}
+% \caption{Experiments on pretraining. All models were trained under the same hyperparameters. PT stands for pretraining and AG stands for augmentation.}
+% \label{result2}
+% \end{table}
+
+\subsubsection{Dataset description}
+We evaluate the model performance on WSIs segmentation using crowdsourced dataset presented in \cite{10.1093/bioinformatics/btz083}.
+This dataset consists of 151 annotated WSIs and corresponding masks with each image's dimension larger than 1024 and each image with different dimensions.
+For more conveninece, we partition all the images into patches of size $1024 \times 1024$.
+After patching, there are a total number of 4235 pairs of RGB image and mask which were split into train-test set using the same ratio as the classification task.
+
+The networks were trained to map pixels into 22 different classes including the outside region of interest (``don't care" class).
+The RGB images and their corresponding masks were 0.23 microns per pixel where each mask pixel values encode region class membership.
+We first implement some existing baseline models including U-Net.
+However, training such a model with input size $(1024 \times 1024)$ requires a lots of computation resources.
+Therefore, we repartition the images into patches of size $(512\times 512)$.
+We also decide to train the proposed method with same input size and patch size of $(128\times 128)$ using transpose convolution reconstruction head.
+In this setting the model performs 1 epoch in every 3 minutes during training.
+
+\subsection{Comparison with state-of-the-arts}
+We will compare our model with 3 state-of-the-art models: (1) UNet \cite{ronneberger2015unet}, (2) UNet with pretrained MobileNetV2 as encoder (UNet-MV2) and (3) TransUNet \cite{chen2021transunet}.
+For all experiments, we applied simple augmentations such as horizontol flip and normalization.
+It took around 3 hours each to train UNet and UNet-MV2 models on TeslaV100 GPU for 15 epochs.
+The segmentation results and model accuracies are shown in Figure \ref{fig:seg} and Table.
+We have yet to include the results from TransUNet due to its long training time (1 hour per epoch) for better convergence.
+
+\begin{figure}[ht]
+\begin{center}
+% \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   \includegraphics[width=0.9\linewidth]{media/Compare.png}
+\end{center}
+   \caption{Segmentation Results (From left to right): WSI, Ground Truth, UNet, UNet-MV2}
+\label{fig:seg}
+% \label{fig:onecol}
+\end{figure}
+
 \begin{table}[ht]
 \centering
-\resizebox{\columnwidth}{!}{\begin{tabular}{c|cccc|c}
+\begin{tabularx}{\columnwidth}{ >{\centering\arraybackslash}X | >{\centering\arraybackslash}X | >{\centering\arraybackslash}X }
 \toprule
-\multirow{2}{*}{Works} & \multicolumn{4}{c|}{Magnification} & \multirow{2}{*}{Mean} \\
- & 40X & 100X & 200X & 400X & \\ \midrule
-PT    & 97.66 & \textbf{98.72} & \textbf{98.01} & \textbf{98.35} & 98.19 \\
-PT+AG & \textbf{99.00} & \textbf{98.72} & \textbf{98.01} & \textbf{98.35} & \textbf{98.52} \\
+Works & Pixel Accuracy & Training Time \newline (minutes) \\
+\midrule
+UNet \cite{ronneberger2015unet}    & 0.67  & 13 \\
+UNet-MV2 & 0.76 & 16 \\
+TransUNet \cite{chen2021transunet} & 0.63 & 63\\
 \bottomrule
-\end{tabular}}
-\caption{Experiments on pretraining. All models were trained under the same hyperparameters. PT stands for pretraining and AG stands for augmentation.}
-\label{result2}
+\end{tabularx}
+\caption{Comparison of pixel accuracy and average training time per epoch for state-of-the-art models}
+\label{seg}
 \end{table}
 
+Due to the computation cost of the baseline approaches, we plan to apply patches based approach which consist of training with input size $(128\times 128)$ and perform inference with images of size $(512\times 512)$ by iterating over patches with recombination after prediction.
+Same as in classification, we will include the evaluation metric results with computational details in our final report.
+
 \section{Conclusion}
-In this stage of work  we proposed a classification model for histological images using ViT architecture.
+In this stage of work we proposed a classification model that achieved a reasonable performance over existing methods.
+Some baseline models were explored for segmentation tasks.
+Some evaluation metrics need to be integerated in the upcoming segmentation experiments, which is underway.
+Moreover, some preliminary experiments with simple upsampling head for segmenetation were not as successful, hence some better architectures should be considered.
+If time permits, creating a stronger image representation with Transformer architecture would be interesting.
+Contrastive learning has shown promises in producing a more robust encodings for downstream tasks.
+
+% \section{Conclusion}
+% In this stage of work  we proposed a classification model for histological images using ViT architecture.
 The proposed method is fast to train and achieved good performance compared to previous works.
@@
 \bibliographystyle{ieee_fullname}
-\bibliography{reference}
-}
+\bibliography{reference}}
 

### 2021-05-25 code/crowdsourcing/conv-free-vit.py

@@ -1,0 +1,519 @@
+import os
+import numpy as np
+import pandas as pd
+from glob import glob
+# import cv2
+from PIL import Image
+# import matplotlib.pyplot as plt
+from tqdm import tqdm
+
+
+import torch
+import torchvision
+import torchvision.transforms as transforms
+import torch.nn.functional as F
+
+from torch import nn, einsum
+from einops import rearrange, repeat
+from einops.layers.torch import Rearrange
+
+from sklearn.model_selection import train_test_split
+from torch.optim.lr_scheduler import StepLR
+from torch.utils.data import DataLoader, Dataset
+from torchvision import datasets
+import torch.optim as optim
+os.environ["CUDA_VISIBLE_DEVICES"] = '0'
+
+class CancerDataset(Dataset):
+
+    def __init__(self, image_dir, mask_dir, transform=None):
+        super(CancerDataset, self).__init__()
+        self.image_dir = image_dir
+        self.image_files = os.listdir(image_dir)
+        self.mask_dir = mask_dir
+        self.transform = transform
+
+    def __len__(self):
+        return len(self.image_files)
+
+    def __getitem__(self, index):
+        image_file = self.image_files[index]
+        mask_file = self.image_files[index]
+        image_path = os.path.join(self.image_dir, image_file)
+        mask_path = os.path.join(self.mask_dir, mask_file)
+        image = Image.open(image_path).convert('RGB')
+        #         image = np.array(image)
+        mask = Image.open(mask_path)
+        mask = np.array(mask)
+        if self.transform:
+            image = self.transform(image)
+
+        label = torch.Tensor(mask).long()
+        return image, label
+
+
+
+
+class Reshape(nn.Module):
+    def __init__(self, mask_size=1024,num_classes=22):
+        super(Reshape, self).__init__()
+        self.mask = mask_size
+        self.num_classes= num_classes
+
+    def forward(self, x):
+        return x.view(-1,self.num_classes,self.mask,self.mask)
+
+class PreNorm(nn.Module):
+    def __init__(self, dim, fn):
+        super().__init__()
+        self.norm = nn.LayerNorm(dim)
+        self.fn = fn
+    def forward(self, x, **kwargs):
+        return self.fn(self.norm(x), **kwargs)
+
+class FeedForward(nn.Module):
+    def __init__(self, dim, hidden_dim, dropout = 0.):
+        super().__init__()
[…]

### 2021-05-25 code/crowdsourcing/knn.py

@@ -1,0 +1,7 @@
+for ex, lb in zip(features, labels):
+        sim = torch.mm(ex.unsqueeze(0), train_features)
+        nbr, ind = sim.topk(k=K, dim=-1)
+        nbr_lab  = torch.gather(train_labels.expand(ex.shape[0], -1), index=ind, dim=-1)
+        unique, lab_cnt  = nbr_lab.unique(return_counts=True)
+        if lb == (unique[torch.argmax(lab_cnt)]):
+            num_correct += 1

### 2021-05-25 code/lightning/arguments.py

@@ -7,8 +7,8 @@ class BaseArgs:
 
     wandb: bool = field(default=False)
 
-    classification: bool=field(default=True)
-    segmentation: bool=field(default=False)
+    classification: bool = field(default=True)
+    segmentation: bool = field(default=False)
 
     amp: bool = field(default=False)
     gpus: str = field(default='1')
@@ -16,6 +16,8 @@ class BaseArgs:
     max_epochs: int = field(default=3)
     batch_size: int = field(default=1)
     drop_rate: int = field(default=0.0)
+
+    scheduler: bool = field(default=False)
 
     learning_rate: float = field(default=1e-5)
     eps: float = field(default=1e-8)
@@ -53,6 +55,8 @@ class ClassificationArgs(BaseArgs):
     pad_mode: str = field(default='constant')
     augmentation: bool = field(default=False)
     train_split: float = field(default=0.7)
+
+    resize: bool = field(default=False)
 
     model_name: str = field(default='vit_base_patch16_224')
     pretrained: bool = field(default=False)

### 2021-05-25 code/lightning/download/download_google.py

@@ -1,0 +1,7 @@
+import gdown
+
+DATA_URL = "https://drive.google.com/u/1/uc?id=1bd60s98V3W00R_N7tvOE5pfoDaf8lpfv&export=download"
+OUTPUT = "combined.tar.gz"
+
+if __name__ == "__main__":
+    gdown.download(DATA_URL, OUTPUT, quiet=False)

### 2021-05-25 code/lightning/main.py

@@ -4,6 +4,7 @@ import timm
 import albumentations as alb
 import pytorch_lightning as pl
 
+from math import ceil
 from torch.utils.data import DataLoader, random_split
 
 from simple_parsing import ArgumentParser
@@ -23,120 +24,139 @@ if __name__ == '__main__':
     args = parser.add_arguments(ClassificationArgs(config=config), dest='options')
     args = parser.parse_args().options
 
-    assert args.magnification in ('40X', '100X', '200X', '400X', 'all')
-    assert args.pad_mode in ('constant', 'reflect', 'reflect_101', 'replicate')
+    if args.classification:
+        assert args.magnification in ('40X', '100X', '200X', '400X', 'all')
+        assert args.pad_mode in ('constant', 'reflect', 'reflect_101', 'replicate')
 
-    height_div = args.image_size[0] // args.patch_size[0]
-    if args.image_size[0] % args.patch_size[0]:
-        height_div += 1
-    width_div = args.image_size[1] // args.patch_size[1]
-    if args.image_size[1] % args.patch_size[1]:
-        width_div += 1
-    input_size = (height_div * args.patch_size[0], width_div * args.patch_size[1])
+        # If resize, resize to given image input size
+        input_size = args.image_size
+        # Otherwise, pad the image to the smallest tiling
+        if not args.resize:
+            # Compute the new image size (will be padded)
+            height_div = ceil(args.image_size[0] / args.patch_size[0])
+            width_div = ceil(args.image_size[1] / args.patch_size[1])
+            input_size = (height_div * args.patch_size[0], width_div * args.patch_size[1])
+        
+        # Model
+        encoder = timm.create_model(
+            args.model_name,
+            pretrained=args.pretrained,
+            num_classes=0,
+            drop_rate=args.drop_rate,
+            img_size=input_size,
+            patch_size=args.patch_size
+        )
+        model = ClassificationModule(encoder, args.num_classes_classification)
 
-    # Model
-    encoder = timm.create_model(
-        args.model_name,
-        pretrained=args.pretrained,
-        num_classes=0,
-        drop_rate=args.drop_rate,
-        img_size=input_size,
-        patch_size=args.patch_size
-    )
-    model = ClassificationModule(encoder, args.num_classes_classification)
+        # Seeding and PL model
+        pl.seed_everything(args.seed, workers=True)
[…]

### 2021-05-25 code/lightning/preprocess.py

@@ -94,41 +94,35 @@ class ClassificationBatchCollector:
     """Batch collector for classification using in DataLoader.collate_fn"""
     def __init__(
         self,
+        image_size  : Tuple[int, int], # This is input size for model
         patch_size  : Tuple[int, int],
-        image_mean  : List[float]=[0.5, 0.5, 0.5],
-        image_std   : List[float]=[0.5, 0.5, 0.5],
         pad_mode    : Optional[str]="constant",
-        do_normalize: Optional[bool]=True,
+        do_resize   : Optional[bool]=False,
         do_augment  : Optional[bool]=False,
-        augmentation: Optional[List["Transform"]]=None
+        transforms  : Optional["Transform"]=None
     ):
+        self.i_h, self.i_w = image_size
         self.p_h, self.p_w = patch_size
-        self.image_mean = np.array(image_mean)
-        self.image_std  = np.array(image_std)
 
         self.pad_mode = getattr(cv2, 'BORDER_{}'.format(pad_mode.upper()))
         assert self.pad_mode in (0, 1, 2, 3, 4)
-        self.do_normalize = do_normalize
+        self.do_resize = do_resize
         self.do_augment = do_augment
-        self.augmentation = augmentation
+        self.transforms = transforms
 
     def __call__(self, batch):
         images, labels = zip(*batch)
-        images = [self.padding(image) for image in images]
-        assert len(set([i.shape for i in images])) == 1
-        if self.do_normalize:
-            images = [self.normalize(image=image)  for image in images]
-        if self.do_augment:
-            images = [self.augmentation(image=image)['image'] for image in images]
+        if not self.do_resize:
+            images = [self.padding(image) for image in images]
+        images = [self.transforms(image=image)['image'] for image in images]
         images = [image.transpose(2, 0, 1) for image in images]
-
         return torch.tensor(images), torch.tensor(labels)
         
     def padding(self, image: "np.ndarray") -> "np.ndarray":
         """Pads image with predefined border type"""
         h, w, _ = image.shape
-        h_to_pad = self.p_h - (h % self.p_h)
-        w_to_pad = self.p_w - (w % self.p_w)
+        h_to_pad = self.i_h - h
+        w_to_pad = self.i_w - w
 
         top, lft = h_to_pad // 2, w_to_pad // 2
         bot, rht = h_to_pad - top, w_to_pad - lft
@@ -139,11 +133,3 @@ class ClassificationBatchCollector:
[…]

### 2021-05-25 code/lightning/scripts/download_breakhis.sh

@@ -1,4 +1,0 @@
-cd timm-fork-install && pip install -e . && cd ..
-mkdir -p data
-echo "Downloading BreakHis Dataset from Google Drive (combined.tar.gz) ..."
-gdown https://drive.google.com/u/1/uc?id=1bd60s98V3W00R_N7tvOE5pfoDaf8lpfv&export=download

### 2021-05-25 code/lightning/timm-fork-install/timm/models/vision_transformer.py

@@ -1,687 +1,0 @@
-""" Vision Transformer (ViT) in PyTorch
-
-A PyTorch implement of Vision Transformers as described in
-'An Image Is Worth 16 x 16 Words: Transformers for Image Recognition at Scale' - https://arxiv.org/abs/2010.11929
-
-The official jax code is released and available at https://github.com/google-research/vision_transformer
-
-DeiT model defs and weights from https://github.com/facebookresearch/deit,
-paper `DeiT: Data-efficient Image Transformers` - https://arxiv.org/abs/2012.12877
-
-Acknowledgments:
-* The paper authors for releasing code and weights, thanks!
-* I fixed my class token impl based on Phil Wang's https://github.com/lucidrains/vit-pytorch ... check it out
-for some einops/einsum fun
-* Simple transformer style inspired by Andrej Karpathy's https://github.com/karpathy/minGPT
-* Bert reference code checks against Huggingface Transformers and Tensorflow Bert
-
-Hacked together by / Copyright 2020 Ross Wightman
-"""
-import math
-import logging
-from functools import partial
-from collections import OrderedDict
-from copy import deepcopy
-
-import torch
-import torch.nn as nn
-import torch.nn.functional as F
-
-from timm.data import IMAGENET_DEFAULT_MEAN, IMAGENET_DEFAULT_STD
-from .helpers import build_model_with_cfg, overlay_external_default_cfg
-from .layers import PatchEmbed, Mlp, DropPath, trunc_normal_, lecun_normal_
-from .registry import register_model
-
-_logger = logging.getLogger(__name__)
-
-
-def _cfg(url='', **kwargs):
-    return {
-        'url': url,
-        'num_classes': 1000, 'input_size': (3, 224, 224), 'pool_size': None,
-        'crop_pct': .9, 'interpolation': 'bicubic', 'fixed_input_size': True,
-        'mean': IMAGENET_DEFAULT_MEAN, 'std': IMAGENET_DEFAULT_STD,
-        'first_conv': 'patch_embed.proj', 'classifier': 'head',
-        **kwargs
-    }
-
-
-default_cfgs = {
-    # patch models (my experiments)
-    'vit_small_patch16_224': _cfg(
[…]
